%-------------------------
% Resume in Latex
% Author : Sarthak
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

% serif
\usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

\begin{center}
    {\Huge \scshape Sarthak Gandhi} \\ \vspace{1pt}
    Toronto, ON \\ \vspace{1pt}
    \small \raisebox{-0.1\height}\faPhone\ 709-325-7081 ~ 
    % \href{mailto:x@gmail.com}
    {\raisebox{-0.2\height}\faEnvelope\  {gandhi.sarthak15@gmail.com}} ~ 
    % \href{https://linkedin.com/in//}
    {\raisebox{-0.2\height}\faLinkedin\ {linkedin.com/in/sarthakgandhi1}}  ~
    % \href{https://github.com/}
    {\raisebox{-0.2\height}\faGithub\ {github.com/sgandhi15}}
    \vspace{-8pt}
\end{center}


% Professional Summmary
\section{Professional Summary}
Experienced Software Developer with a Master's degree in Computer Engineering. Proficient in developing scalable software solutions with strong skills in data structures, algorithms, and object-oriented design. Effective team collaborator, contributing to all stages of software development. Dedicated to using technology for innovation and positive impact, seeking growth in a dynamic environment focused on customer and employee success.
\vspace{-8pt}

\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
\small{\item{
\textbf{Programming Languages}{: JavaScript, Python, SQL, Java, Go} \\
\textbf{Frontend/Backend}{: React, NextJS, NodeJS, ExpressJS, NestJS, REST APIs, Web3.js} \\
\textbf{Databases}{: PostgreSQL, MongoDB} \\
\textbf{Tools/Technologies}{: Git, NginX, Linux(Unix Utilities), AWS (Amazon Web Services)(EC2, S3)} \\
\textbf{Soft Skills}{: Adaptability, Team Collaboration, Problem Solving, Communication, Adaptability, Customer Focus} \\
}}
\end{itemize}
\vspace{-16pt}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {MainOnePro}{02/2024 - 04/2024}
      {Full Stack Developer}{St. John's, NL}
      \resumeItemListStart
        \resumeItem{Developed and deployed web app with secure authentication and payments, increasing user engagement by 10\%.}
        \resumeItem{Reduced delivery timelines by 6\%, enhancing project throughput and meeting Service Level Agreements (SLA’s).}
        \resumeItem{Ensured data security and integrity for sensitive transactions.}
        \resumeItem{Aligned project goals with business objectives, resulting in a 15\% increase in stakeholder satisfaction.}
        \resumeItem{Mentored two junior developers, improving their skills and productivity.}
      \resumeItemListEnd
    \resumeSubheading
      {Creadigol Solution}{12/2020 - 8/2022}
      {Full Stack Developer}{Vadodara, India}
      \resumeItemListStart
        \resumeItem{Led team in developing REST APIs and single-page applications, boosting client Net Promoter Score by 20\%.}
        \resumeItem{Enhanced platform security and reliability by implementing robust authentication and payment systems.}
        \resumeItem{Collaborated with stakeholders for customized solutions, resulting in a 26\% improvement in UI responsiveness.}
        \resumeItem{Introduced automated testing procedures, reducing software bugs and errors by 33\%.}
        \resumeItem{Streamlined deployment processes, resulting in a 29\% reduction in deployment time and improved efficiency.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd
\vspace{-16pt}
%-----------PROJECTS-----------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeProjectHeading
        {\textbf{GM Dynasty} - \emph{React, TypeScript, NodeJS, ExpressJS, PostgreSQL}}{04/2022 - 07/2022}
        \resumeItemListStart
          \resumeItem{Engineered responsive profile management system, reducing load times by 30\%.}
          \resumeItem{Ensured data integrity and security for over 7k+ user profiles, integrating PostgreSQL with Node.js.}
          \resumeItem{Implemented streamlined user registration process, resulting in a 25\% increase in user sign-ups.}
          \resumeItem{Enhanced user profile customization options, leading to a 20\% increase in user satisfaction.}
        \resumeItemListEnd
        \vspace{-16pt}
    \resumeProjectHeading
        {\textbf{Santa Cars} - \emph{React, NodeJS, TypeScript, Redux, ExpressJS, Web3.js, MongoDB}}{02/2021 - 08/2021}
        \resumeItemListStart
          \resumeItem{Developed NFT gaming platform, increasing user engagement by 30\% with React and Web3.js.}
          \resumeItem{Established secure transaction environment, integrating advanced authentication mechanisms.}
          \resumeItem{Implemented real-time chat feature, enhancing user interaction and satisfaction.}
          \resumeItem{Enhanced platform scalability, accommodating 50\% increase in user traffic.}
        \resumeItemListEnd
                \vspace{-16pt}
    \resumeProjectHeading
        {\textbf{Kiderra} - \emph{NextJS, NodeJS, ExpressJS, PostgreSQL}}{02/2024 - 04/2024}
        \resumeItemListStart
          \resumeItem{Directed MVP web app development, ensuring robust security measures, reducing vulnerabilities by 25\%.}
          \resumeItem{Facilitated team collaboration for aligned project scope, boosting efficiency by 30\%.}
          \resumeItem{Enhanced Kiderra's service accessibility with user-friendly interface updates, increasing engagement by 40\%.}
          \resumeItem{Streamlined project delivery, reducing time to market by 20\%.}
        \resumeItemListEnd
  \resumeSubHeadingListEnd
\vspace{-15pt}

%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
{Master of Applied Science in Computer Engineering}{09/2022 - 04/2024}
{Memorial University of Newfoundland}{St. John's, NL}
\resumeSubheading
{Bachelor of Engineering in Computer Science}{08/2017 - 05/2021}
{Babaria Institute of Technology}{Vadodara, India}
\resumeSubHeadingListEnd
%-----------INVOLVEMENT---------------
\section{Leadership / Extracurricular}
    \resumeSubHeadingListStart
        \resumeSubheading{Canada Learning Code}{01/2024 - Present}{Instructor}{}
    \resumeSubHeadingListEnd


\end{document}

